ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-11-15 pyked.tex
add "experiments" to footnote about RCM & ST time-histories plan

Rapid compression machine experiments typically report several additional pieces of information in
addition to the ignition delay. As for shock tube experiments, these describe some of the
facility-specific effects during an experiment. The keys to describe this information are:
%
\begin{itemize}
    \item \yabox|volume-history| (optional, mapping): Specify the volume history of the reaction
    chamber as a function of time during a rapid compression machine experiment. The fields in this
    mapping are:
    \begin{itemize}
        \item \yabox|volume| (required, mapping): A mapping describing the volume in the history.
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the volume, with dimensions length
            cubed
            \item \yabox|column| (required, integer): the \deletetwo{0-based} \addtwo{zero-based} index of the column storing the
            volume information in the \yabox|values| array \addtwo{(e.g., 0 or 1)}
        \end{itemize}
        \item \yabox|time| (required, mapping): A mapping describing the time in the history.
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the time
            \item \yabox|column| (required, integer): the \deletetwo{0-based} \addtwo{zero-based} index of the column storing the
            time information in the \yabox|values| array \addtwo{(e.g., 0 or 1)}
        \end{itemize}
        \item \yabox|values| (required, sequence): A \deletetwo{sequence of sequences describing the values of
        the volume at the time points.}\addtwo{sequence of time-volume pairs describing the values
        of the volume at different times}
    \end{itemize}
    \item \yabox|compressed-temperature| (optional, sequence): The estimated temperature at the end
    of the compression stroke
    \item \yabox|compression-time| (optional, sequence): The time taken during the compression
    stroke
    \item \yabox|compressed-pressure| (optional, sequence): The measured pressure at the end of the
    compression stroke
\end{itemize}

>>>>

Rapid compression machine experiments typically report several additional pieces of information in
addition to the ignition delay. As for shock tube experiments, these describe some of the
facility-specific effects during an experiment. The keys to describe this information are:
%
\begin{itemize}
    \item \yabox|volume-history| (optional, mapping): Specify the volume history of the reaction
    chamber as a function of time during a rapid compression machine experiment. The fields in this
    mapping are:
    \begin{itemize}
        \item \yabox|volume| (required, mapping): A mapping describing the volume in the history\footnote{\addtwo{Future versions
        of \ck{} will support specifying additional time histories for rapid compression machine and shock tube
        experiments (e.g., pressure, volume, light emission, OH emission). These will follow the specification format given for volume.}}
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the volume, with dimensions length
            cubed
            \item \yabox|column| (required, integer): the \deletetwo{0-based} \addtwo{zero-based} index of the column storing the
            volume information in the \yabox|values| array \addtwo{(e.g., 0 or 1)}
        \end{itemize}
        \item \yabox|time| (required, mapping): A mapping describing the time in the history.
        The fields in this mapping are:
        \begin{itemize}
            \item \yabox|units| (required, string): the units of the time
            \item \yabox|column| (required, integer): the \deletetwo{0-based} \addtwo{zero-based} index of the column storing the
            time information in the \yabox|values| array \addtwo{(e.g., 0 or 1)}
        \end{itemize}
        \item \yabox|values| (required, sequence): A \deletetwo{sequence of sequences describing the values of
        the volume at the time points.}\addtwo{sequence of time-volume pairs describing the values
        of the volume at different times}
    \end{itemize}
    \item \yabox|compressed-temperature| (optional, sequence): The estimated temperature at the end
    of the compression stroke
    \item \yabox|compression-time| (optional, sequence): The time taken during the compression
    stroke
    \item \yabox|compressed-pressure| (optional, sequence): The measured pressure at the end of the
    compression stroke
\end{itemize}
